Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
blah sur widening non monotone

\MM{Peut-être dire quelque part vers ici que le widening n'est en
  général pas monotone, et que donc on ne peut jamais rien dire en
  théorie sur la précision vu qu'être plus précis à une itération peut
  faire perdre en précision la suivante ...}

@@

>>>>

@@

Widening operations have a somewhat counterintuitive behavior: the result of an analysis (postcondition) is not necessarily monotonic with respect to the precondition. For instance, classical interval analysis with widening and decreasing iterations on the following loop yields a loop invariant $x \in [0,+\infty)$ if the precondition is $x \in [0,0]$ , but $x \in [0,10]$ (strictly stronger) if the precondition is $x \in [0,10]$ (strictly weaker):
\lstinline|while (x != 10) x=x+1;|.
This means that, when using widenings, being locally more precise (for instance, by using more expressive abstract domains, or widening operators that climb more slowly \cite{BagnaraHRZ05SCP}) does not necessarily translate into higher final precision.
It is almost always possible to concoct examples where a supposedly more precise abstraction (e.g. polyhedra) yields less precise results than a less precise one (e.g. intervals), but are these examples representative of real programs?
This justifies our recourse to evaluation on realistic examples~(\S~\ref{sec:compare_techniques}).
